Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-04-06 introduction/Subsections/Introduction.tex
Updates from Overleaf

The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study. Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.

>>>>

The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study. Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}\cite{, yet remains a vast open challenge.

### 2023-04-06 introduction/Subsections/Motivation.tex
Updates from Overleaf

\section{About music aural skills and high-level perception}

@@

\begin{figure}[h]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
\end{figure}

@@

Anstieg (Initial Ascent): Ascending motion leading to the primary tone of the fundamental line.
Arpeggiation (Brechung): Elementary elaboration of a harmony.
Background (Hintergrund): The structural level of the fundamental structure.
Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forming the harmonic content of the background of tonal musical pieces.
Chord of Nature (Klang): The complex sound consisting of the first five notes of the harmonic series, suggesting a model for the major triad.
Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
Foreground (Vordergrund): The surface level of musical structure in Schenkerian analysis.
Fundamental Line (Urlinie): The melodic aspect of the fundamental structure, a stepwise descent from one of the triad notes to the tonic.
Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad is able to govern spans of music when not physically sounding.
Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middleground, and foreground.
Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space that is filled with passing and neighbor notes.
Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
Voice Leading: The study of the principles that govern the progression of the component voices of a composition both separately and in combination.
The glossary also includes related articles, references, and external links for further reading and understanding of Schenkerian analysis.

>>>>

\section{About music aural skills and high-level perceptual concepts}

@@

\begin{figure}[ht]
\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
\end{figure}

@@

Anstieg (Initial Ascent): Ascending motion leading to the primary tone of the fundamental line.
Arpeggiation (Brechung): Elementary elaboration of a harmony.
Background (Hintergrund): The structural level of the fundamental structure.
Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forms the harmonic content of the background of tonal musical pieces.
Chord of Nature (Klang): The complex sound consisting of the first five harmonic series notes suggests a model for the major triad.
Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
Foreground (Vordergrund): The surface level of musical structure in Schenkerian analysis.
Fundamental Line (Urlinie): The melodic aspect of the fundamental structure, a stepwise descent from one of the triad notes to the tonic.
Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad can govern music spans when not physically sounding.
Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middle-ground, and foreground.
Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space filled with passing and neighbor notes.
Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
Voice Leading: The study of the principles that govern the progression of the component voices of the composition both separately and in combination.
The glossary also includes related articles, references, and external links for further reading and understanding Schenkerian analysis.
